---
title: "Time Series Data Analysis on Temperature"
author: "Temperature Data"
date: " "
output: 
   html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("E:\\29-09-2021_1\\Data to Merge")
```

```{r packages, echo=FALSE,message=FALSE, include=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(readr)
library(rmarkdown)
library(bigmemory)
library(biganalytics)
library(bigtabulate)
```

# Introduction

## Data Merging
The different but common data were merged together to form a one data frame. There were 25 CSV files in total with 8 major categories. The categories and the total number of files, and the total rows after merging. After merging we obtained 8 major data sets.

### Merged data sets
 - Air Sun Shade (3: 292452)
 - Big Mine Sunshine (3: 445563 )
 - Evacuated tube (5: 793271)
 - Little Mine (3: 345873)
 - Super Big Mine (3: 371060)
 - One Split (3: 445407)
 - Pool Heater (2: 335270)
 - Pool Pit (3: 416003)

## Time Series Plots
There are 8 plots that are based on the 8 merged data sets. The plots are responsive per the use requirement. The user can view the time series plot for one temperature performance at a go, by clicking on the legend. Clicking the legend will make one plot to disappear, and after clicking it again, the plot will appear.

### Air Sun Shade

The number of rows for the Air Sun Shade data set:
```{r, echo=FALSE}
df_AirSunShade <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\AirSunShade", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
nrow(df_AirSunShade)
```

The variable names for the Air Sun Shade are as follows:
```{r,echo=FALSE}
colnames(df_AirSunShade)
```


```{r,echo=FALSE}
AirSunShade <- df_AirSunShade%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test1 <- AirSunShade%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test1 <- data.frame(test1)
nrow(test1)
```

#### Statistics

```{r one, echo=FALSE}
FirstReading <-max(na.omit(df_AirSunShade$DateTime))
LastReading <-  min(na.omit(df_AirSunShade$DateTime)) 
Minimum <- min(na.omit(AirSunShade$Temperature1))
Maximum <- max(na.omit(AirSunShade$Temperature1))
Average <- mean(na.omit(AirSunShade$Temperature1))
StandardDeviation <- sd(na.omit(AirSunShade$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r two, echo=FALSE}
Minimum <- min(na.omit(AirSunShade$Temperature2))
Maximum <- max(na.omit(AirSunShade$Temperature2))
Average <- mean(na.omit(AirSunShade$Temperature2))
StandardDeviation <- sd(na.omit(AirSunShade$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)

```

```{r,echo=FALSE}
dates <- unique(sort(test1$DateTime))
Date = factor(test1$DateTime, labels = dates,ordered = T)
p1 <- ggplot(test1,aes(x = Date)) +
  geom_line(aes(y=temperature1,group = 1,color = "ShadeTemperature")) +
  geom_line(aes(y=temperature2,group = 1,color = "SunTemperature"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("Air Sun Shade")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(p1, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
```

### Big Mine Sunshine

The number of rows for the Big Mine Sunshine data set:
```{r, echo=FALSE}
df_BigMineSunshine <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\bigMineSunshine", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
nrow(df_BigMineSunshine)
#df_BigMineSunshine <- na.omit(df_BigMineSunshine)
```

The variable names for the Air Sun Shade are as follows:
```{r,echo=FALSE}
colnames(df_BigMineSunshine)
```


```{r,echo=FALSE}
BigMineSunshine <- df_BigMineSunshine%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test2 <- BigMineSunshine%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test2 <- data.frame(test2)
nrow(test2)
```

#### Statistics

```{r, echo=FALSE}
FirstReading <-max(na.omit(df_BigMineSunshine$DateTime))
LastReading <-  min(na.omit(df_BigMineSunshine$DateTime)) 
Minimum <- min(na.omit(BigMineSunshine$Temperature1))
Maximum <- max(na.omit(BigMineSunshine$Temperature1))
Average <- mean(na.omit(BigMineSunshine$Temperature1))
StandardDeviation <- sd(na.omit(BigMineSunshine$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r, echo=FALSE}
Minimum <- min(na.omit(BigMineSunshine$Temperature2))
Maximum <- max(na.omit(BigMineSunshine$Temperature2))
Average <- mean(na.omit(BigMineSunshine$Temperature2))
StandardDeviation <- sd(na.omit(BigMineSunshine$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)
```

```{r,echo=FALSE}
dates <- unique(sort(test2$Date))
Date = factor(test2$Date, labels = dates,ordered = T)
p2 <- ggplot(test2,aes(x=Date))+
  geom_line(aes(y=temperature1,group = 1,color = "topTemperature")) +
  geom_line(aes(y=temperature2,group = 1,color = "bottomTemperature"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("Big Mine Sunshine")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(p2, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
```


### Evacuated tube

The number of rows for the Evacuated tube data set:
```{r, echo=FALSE}
df_Evacuatedtube <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\Evacuatedtube", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
nrow(df_Evacuatedtube)
#df_BigMineSunshine <- na.omit(df_BigMineSunshine)
```

The variable names for the Evacuated tube Shade are as follows:
```{r,echo=FALSE}
colnames(df_Evacuatedtube)
```



```{r,echo=FALSE}
Evacuatedtube <- df_Evacuatedtube%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test3 <- Evacuatedtube%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test3 <- data.frame(test3)
nrow(test3)
```


#### Statistics

```{r, echo=FALSE}
FirstReading <-max(na.omit(df_Evacuatedtube$DateTime))
LastReading <-  min(na.omit(df_Evacuatedtube$DateTime)) 
Minimum <- min(na.omit(Evacuatedtube$Temperature1))
Maximum <- max(na.omit(Evacuatedtube$Temperature1))
Average <- mean(na.omit(Evacuatedtube$Temperature1))
StandardDeviation <- sd(na.omit(Evacuatedtube$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r, echo=FALSE}
Minimum <- min(na.omit(Evacuatedtube$Temperature2))
Maximum <- max(na.omit(Evacuatedtube$Temperature2))
Average <- mean(na.omit(Evacuatedtube$Temperature2))
StandardDeviation <- sd(na.omit(Evacuatedtube$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)

```


```{r,echo=FALSE}
dates <- unique(sort(test3$Date))
Date = factor(test3$Date, labels = dates,ordered = T)
p3 <- ggplot(test3,aes(x=Date)) +
  geom_line(aes(y=temperature1,group = 1,color = "end Of Exchanger Temperature")) +
  geom_line(aes(y=temperature2,group = 1,color = "tank Temperature"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("Evacuated tube")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(p3, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
```



### Little Mine

The number of rows for the Little Mine data set:
```{r, echo=FALSE}
df_LittleMine <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\LittleMine", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
class(df_LittleMine)
nrow(df_LittleMine)
#df_LittleMine1 <- na.omit(df_LittleMine)
```

The variable names for the Evacuated tube Shade are as follows:
```{r,echo=FALSE}
colnames(df_LittleMine)
```

```{r,echo=FALSE}
LittleMine <- df_LittleMine%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test4 <- LittleMine%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test4 <- data.frame(test4)
nrow(test4)
```


#### Statistics

```{r, echo=FALSE}
FirstReading <- max(na.omit(df_LittleMine$DateTime))
LastReading <- min(na.omit(df_LittleMine$DateTime)) 
Minimum <- min(na.omit(LittleMine$Temperature1))
Maximum <- max(na.omit(LittleMine$Temperature1))
Average <- mean(na.omit(LittleMine$Temperature1))
StandardDeviation <- sd(na.omit(LittleMine$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r, echo=FALSE}
Minimum <- min(na.omit(LittleMine$Temperature2))
Maximum <- max(na.omit(LittleMine$Temperature2))
Average <- mean(na.omit(LittleMine$Temperature2))
StandardDeviation <- sd(na.omit(LittleMine$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)

```


```{r,echo=FALSE}
dates <- unique(sort(test4$Date))
Date = factor(test4$Date, labels = dates,ordered = T)
p4 <- ggplot(test4,aes(x = Date)) +
  geom_line(aes(y=temperature1,group = 1,color = "evacuated Tube Temperature")) +
  geom_line(aes(y=temperature2,group = 1,color = "little Mine Temperature"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("Little Mine")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(p4, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
```


### Super Big Mine

The number of rows for the Super Big Mine data set:
```{r, echo=FALSE}
df_Superbigmine <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\Superbigmine", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
class(df_Superbigmine)
nrow(df_Superbigmine)
#df_LittleMine1 <- na.omit(df_LittleMine)
```

The variable names for the Evacuated tube Shade are as follows:
```{r,echo=FALSE}
colnames(df_Superbigmine)
```


```{r,echo=FALSE}
Superbigmine <- df_Superbigmine%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test5 <- Superbigmine%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test5 <- data.frame(test5)
nrow(test5)
```


#### Statistics

```{r, echo=FALSE}
FirstReading <- max(na.omit(df_Superbigmine$DateTime))
LastReading <- min(na.omit(df_Superbigmine$DateTime)) 
Minimum <- min(na.omit(Superbigmine$Temperature1))
Maximum <- max(na.omit(Superbigmine$Temperature1))
Average <- mean(na.omit(Superbigmine$Temperature1))
StandardDeviation <- sd(na.omit(Superbigmine$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r, echo=FALSE}
Minimum <- min(na.omit(Superbigmine$Temperature2))
Maximum <- max(na.omit(Superbigmine$Temperature2))
Average <- mean(na.omit(Superbigmine$Temperature2))
StandardDeviation <- sd(na.omit(Superbigmine$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)

```


```{r,echo=FALSE}
dates <- unique(sort(test5$Date))
Date = factor(test5$Date, labels = dates,ordered = T)
p5 <- ggplot(test5,aes(x = Date)) +
  geom_line(aes(y=temperature1,group = 1,color = "Temperature1")) +
  geom_line(aes(y=temperature2,group = 1,color = "Temperature2"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("Super Big Mine")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(p5, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
```



### One Split

The number of rows for the One Split data set:
```{r, echo=FALSE}
df_OneSplit <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\OneSplit", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
class(df_OneSplit)
nrow(df_OneSplit)
#df_LittleMine1 <- na.omit(df_LittleMine)
```

The variable names for the Evacuated tube Shade are as follows:
```{r,echo=FALSE}
colnames(df_OneSplit)
```

```{r,echo=FALSE}
OneSplit <- df_OneSplit%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test6 <- OneSplit%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test6 <- data.frame(test6)
nrow(test6)
```


#### Statistics

```{r, echo=FALSE}
FirstReading <- max(na.omit(df_OneSplit$DateTime))
LastReading <- min(na.omit(df_OneSplit$DateTime)) 
Minimum <- min(na.omit(OneSplit$Temperature1))
Maximum <- max(na.omit(OneSplit$Temperature1))
Average <- mean(na.omit(OneSplit$Temperature1))
StandardDeviation <- sd(na.omit(OneSplit$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r, echo=FALSE}
Minimum <- min(na.omit(OneSplit$Temperature2))
Maximum <- max(na.omit(OneSplit$Temperature2))
Average <- mean(na.omit(OneSplit$Temperature2))
StandardDeviation <- sd(na.omit(OneSplit$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)

```

```{r,echo=FALSE}
dates <- unique(sort(test6$Date))
Date = factor(test6$Date, labels = dates,ordered = T)
p6 <- ggplot(test6,aes(x = Date)) +
  geom_line(aes(y=temperature1,group = 1,color = "Temperature1")) +
  geom_line(aes(y=temperature2,group = 1,color = "Temperature2"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("One Split")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(p6, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
```




### Pool Heater

The number of rows for the Pool Heater data set:
```{r, echo=FALSE}
df_PoolHeater <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\PoolHeater", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
class(df_PoolHeater)
nrow(df_PoolHeater)
#df_LittleMine1 <- na.omit(df_LittleMine)
```

The variable names for the Evacuated tube Shade are as follows:
```{r,echo=FALSE}
colnames(df_PoolHeater)
```


```{r,echo=FALSE}
PoolHeater <- df_PoolHeater%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test7 <- PoolHeater%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test7 <- data.frame(test7)
nrow(test7)
```


#### Statistics

```{r, echo=FALSE}
FirstReading <- max(na.omit(df_PoolHeater$DateTime))
LastReading <- min(na.omit(df_PoolHeater$DateTime)) 
Minimum <- min(na.omit(PoolHeater$Temperature1))
Maximum <- max(na.omit(PoolHeater$Temperature1))
Average <- mean(na.omit(PoolHeater$Temperature1))
StandardDeviation <- sd(na.omit(PoolHeater$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r, echo=FALSE}
Minimum <- min(na.omit(PoolHeater$Temperature2))
Maximum <- max(na.omit(PoolHeater$Temperature2))
Average <- mean(na.omit(PoolHeater$Temperature2))
StandardDeviation <- sd(na.omit(PoolHeater$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)

```


```{r,echo=FALSE}
dates <- unique(sort(test7$Date))
Date = factor(test7$Date, labels = dates,ordered = T)
p7 <- ggplot(test7,aes(x=Date)) +
  geom_line(aes(y=temperature1,group = 1,color = "Temperature1")) +
  geom_line(aes(y=temperature2,group = 1,color = "Temperature2"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("Pool Heater")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(p7, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
```


### Pool Pit

The number of rows for the Pool Pit data set:
```{r, echo=FALSE}
df_PoolPit <- list.files(path="E:\\29-09-2021_1\\Data to Merge\\PoolPit", pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read.csv) %>%
  bind_rows
class(df_PoolPit)
nrow(df_PoolPit)
#df_LittleMine1 <- na.omit(df_LittleMine)
```

The variable names for the Evacuated tube Shade are as follows:
```{r,echo=FALSE}
colnames(df_PoolPit)
```


```{r,echo=FALSE}
PoolPit <- df_PoolPit%>%
  select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)
```

```{r, echo=FALSE}
test8 <- PoolPit%>%
   select(DateTime,Date,Month,Year, Temperature1, Temperature2)%>%
  group_by(Month,Date)%>%
  summarise(temperature1 = round(mean(Temperature1),2),
            temperature2 = round(mean(Temperature2),2))
test8 <- data.frame(test8)
nrow(test8)
```


#### Statistics

```{r, echo=FALSE}
FirstReading <- max(na.omit(df_PoolPit$DateTime))
LastReading <- min(na.omit(df_PoolPit$DateTime)) 
Minimum <- min(na.omit(PoolPit$Temperature1))
Maximum <- max(na.omit(PoolPit$Temperature1))
Average <- mean(na.omit(PoolPit$Temperature1))
StandardDeviation <- sd(na.omit(PoolPit$Temperature1))


rbind(FirstReading,LastReading,Minimum,Maximum,Average,StandardDeviation)

```

```{r, echo=FALSE}
Minimum <- min(na.omit(PoolPit$Temperature2))
Maximum <- max(na.omit(PoolPit$Temperature2))
Average <- mean(na.omit(PoolPit$Temperature2))
StandardDeviation <- sd(na.omit(PoolPit$Temperature2))


rbind(Minimum,Maximum,Average,StandardDeviation)

```


```{r,echo=FALSE}
dates <- unique(sort(test8$Date))
Date = factor(test8$Date, labels = dates,ordered = T)
p8 <- ggplot(test8,aes(x=Date)) +
  geom_line(aes(y=temperature1,group = 1,color = "Temperature1")) +
  geom_line(aes(y=temperature2,group = 1,color = "Temperature2"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("Pool Pit")+
  theme(plot.title = element_text(hjust = 0.5))

p88<-ggplotly(p8, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")
p88
```


### All Data Sets and Plots

The number of rows for the Pool Pit data set:
```{r, echo=FALSE,include=FALSE}
df_AirSunShade
df_BigMineSunshine
df_Evacuatedtube 
df_LittleMine 
df_Superbigmine 
df_OneSplit 
df_PoolHeater 
df_PoolPit
```

```{r,  echo=FALSE,include=FALSE}
test1
test2
test3
test4
test5
test6
test7
test8
```

```{r, echo=FALSE}
test9 <- cbind(
  test1[1:214,]
,test2[1:214,]
,test3[1:214,]
,test4[1:214,]
,test5[1:214,]
,test6[1:214,]
,test7[1:214,]
,test8[1:214,])

names(test9)[3] <- "Temp11"
names(test9)[4] <- "Temp12"
names(test9)[7] <- "Temp21"
names(test9)[8] <- "Temp22"
names(test9)[11] <- "Temp31"
names(test9)[12] <- "Temp32"
names(test9)[15] <- "Temp41"
names(test9)[16] <- "Temp42"
names(test9)[19] <- "Temp51"
names(test9)[20] <- "Temp52"
names(test9)[23] <- "Temp61"
names(test9)[24] <- "Temp62"
names(test9)[27] <- "Temp71"
names(test9)[28] <- "Temp72"
names(test9)[31] <- "Temp81"
names(test9)[32] <- "Temp82"
names(test9)[2] <- "Date1"

test9 = subset(test9, select = c(Date1,Temp11,Temp12,Temp21,Temp22,Temp31,Temp32,Temp41,Temp42,Temp51,Temp52,Temp61,Temp62,Temp71,Temp72,Temp81,Temp82) )

#head(test9)
```

```{r, echo=FALSE}
dates <- unique(sort(test9$Date1))
Date1 = factor(test9$Date1, labels = dates,ordered = T)
pal <- ggplot(test9,aes(x=Date1)) +
  geom_line(aes(y=Temp11,group = 1,color = "Air Sun Shade1")) +
  geom_line(aes(y=Temp12,group = 1,color = "Air Sun Shade2")) +
  geom_line(aes(y=Temp21,group = 1,color = "Big Mine Sun Shine1")) +
  geom_line(aes(y=Temp22,group = 1,color = "Big Mine Sun Shine2")) +
  geom_line(aes(y=Temp31,group = 1,color = "Evacuated tube1")) +
  geom_line(aes(y=Temp32,group = 1,color = "Evacuated tube2")) +
  geom_line(aes(y=Temp41,group = 1,color = "Little Mine1")) +
  geom_line(aes(y=Temp42,group = 1,color = "Little Mine2")) +
  geom_line(aes(y=Temp51,group = 1,color = "Super Big Mine1")) +
  geom_line(aes(y=Temp52,group = 1,color = "Super Big Mine2")) +
  geom_line(aes(y=Temp61,group = 1,color = "One Spli1")) +
  geom_line(aes(y=Temp62,group = 1,color = "One Split2")) +
  geom_line(aes(y=Temp71,group = 1,color = "Pool Heater1")) +
  geom_line(aes(y=Temp72,group = 1,color = "Pool Heater2")) +
  geom_line(aes(y=Temp81,group = 1,color = "Pool Pit1"))+
  geom_line(aes(y=Temp82,group = 1,color = "Pool Pit2"))+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))+
  xlab("Date")+ ylab("Temperature 0C") +
  ggtitle("All Temperature Plots")+
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(pal, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x")

```



